\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-20 paper.qmd
Add error calculation

The prediction approach involves performing the K-nearest neighbors (KNN) algorithm for an unsupervised classification problem. First, the nearest \pD{} model point is identified for a given new \pD{} point. Then, the corresponding \gD{} centroid mapping for the identified \pD{} model point is determined. Finally, the coordinates of this \gD{} centroid are used as the predicted \gD{} embedding for the new \pD{} data point. This step is particularly valuable due to the limitations of some NLDR techniques, like tSNE, which don't provide a straightforward method for prediction. As a result, our approach offers a solution that capable of generating predicted \gD{} embedding regardless of the NLDR technique employed, effectively addressing this functional gap.

@@

Residuals are essential for evaluating the accuracy of representing high-D points by the high-D mapping of 2D bin centroids. To measure this accuracy, an error metric is introduced, quantifying the sum of squared differences between the high-D data ($x_{ij}$) and the high-D mapping of the 2D bin centroid data ($C_{x_ij}$) across all observations and dimensions (see @eq-equation10).

$$
\text{Error} = \sum_{j = 1}^{n}\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2
$$ {#eq-equation10}

Here, $n$ represents the number of observations, $p$ represents the dimensions of high-D data, $x_{ij}$ is the high-D data, and $C_{x_ij}$ is the high-D mapping of the 2D bin centroid.

To assess how well our method captures and represents the underlying structure of the high-D data, Mean Squared Error (MSE) is used. When computing MSE, total model error (see @sec-summary) is divided by the number of observations to make it as a mean value (see @eq-equation9).

$$
\text{MSE} = \sum_{j = 1}^{n} \frac{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}{n}
$$ {#eq-equation9}

>>>>

The prediction approach involves performing the K-nearest neighbors (KNN) algorithm for an unsupervised classification problem. First, the nearest \pD{} model point is identified for a given new \pD{} point. Then, the corresponding \kD{} centroid mapping for the identified \pD{} model point is determined. Finally, the coordinates of this \kD{} centroid are used as the predicted \kD{} embedding for the new \pD{} data point. .

@@

To assess how well our method captures and represents the underlying structure of the \pD{} data, residuals are important. Residuals are computed by taking the squared \pD{} Euclidean distance, $\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{x_ij})^2$. Additionally, Mean Squared Error (MSE), $\sum_{i = 1}^{n}\sum_{j = 1}^{p} \frac{(x_{ij} - C^{(p)}_{x_ij})^2}{n}$, is computed based on residuals.

### 2024-05-20 paper.tex
Add error calculation

Residuals are essential for evaluating the accuracy of representing
high-D points by the high-D mapping of 2D bin centroids. To measure this
accuracy, an error metric is introduced, quantifying the sum of squared
differences between the high-D data (\(x_{ij}\)) and the high-D mapping
of the 2D bin centroid data (\(C_{x_ij}\)) across all observations and
dimensions (see Equation~\ref{eq-equation10}).

\begin{equation}\phantomsection\label{eq-equation10}{
\text{Error} = \sum_{j = 1}^{n}\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2
}\end{equation}

Here, \(n\) represents the number of observations, \(p\) represents the
dimensions of high-D data, \(x_{ij}\) is the high-D data, and
\(C_{x_ij}\) is the high-D mapping of the 2D bin centroid.

To assess how well our method captures and represents the underlying
structure of the high-D data, Mean Squared Error (MSE) is used. When
computing MSE, total model error (see Section~\ref{sec-summary}) is
divided by the number of observations to make it as a mean value (see
Equation~\ref{eq-equation9}).

\begin{equation}\phantomsection\label{eq-equation9}{
\text{MSE} = \sum_{j = 1}^{n} \frac{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}{n}
}\end{equation}

>>>>

To assess how well our method captures and represents the underlying
structure of the \pD{} data, residuals are important. Residuals are
computed by taking the squared \pD{} Euclidean distance,
\(\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{x_ij})^2\).
Additionally, Mean Squared Error (MSE),
\(\sum_{i = 1}^{n}\sum_{j = 1}^{p} \frac{(x_{ij} - C^{(p)}_{x_ij})^2}{n}\),
is computed based on residuals.
